---
title: "R Notebook"
output: html_notebook
---



Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

(a) Check if there are any missing values.

```{r}
#file.choose()
load("C:/Proyectos ML/Mineria/Hands_On_2/carInsurance.Rdata" )
ls()

```

(b) Count the number of cases that have, at least, one missing value


```{r}
library(dplyr)
#file.choose()

load("C:/Proyectos ML/Mineria/Hands_On_2/carInsurance.Rdata")

# Verificar los objetos cargados
ls()
# Leer el objeto como un data frame
data <- as.data.frame(carIns)
filtered_data <- data %>% filter(rowSums(is.na(.)) > 0)
print(filtered_data)
```

(c) Create a new data set by removing all the cases that have missing values.

```{r}
library(dplyr)
#file.choose()
load("C:/Proyectos ML/Mineria/Hands_On_2/carInsurance.Rdata")
df <- as.data.frame(carIns)
filtra <- df[complete.cases(df) ==  TRUE,]
print(filtra)

eliminar_na <- na.omit(df)
#print(eliminar_na)
save(eliminar_na, file = "nueva_data1.Rdata" )
print(eliminar_na)
```
(d) Create a new data set by imputing all the missing values with 0.


```{r}

library(dplyr)

load("C:/Proyectos ML/Mineria/Hands_On_2/carInsurance.Rdata")
mi_df <- as.data.frame(carIns)
valor_entero <- mi_df
valor_entero[is.na(valor_entero)] <- 0 
print(valor_entero)
save(valor_entero, file = 'Nuevo_set.Rdata')

load('C:/Proyectos ML/Mineria/Hands_On_2/Nuevo_set.Rdata')
print(as.data.frame(valor_entero))

#REVISAR
#columna_nDoors <- subset(valor_entero, select = nDoors)
#print(columna_nDoors)
#char_data <- as.character(levels(columna_nDoors))
#char_levels <- as.character(levels(char_data))
```
(e) Create a new data set by imputing the mean in all the columns which have double type values



```{r}

load("C:/Proyectos ML/Mineria/Hands_On_2/nueva_data1.Rdata")

data <- as.data.frame(eliminar_na)
# Seleccionar solo las columnas numéricas
columnas_numericas <- sapply(data, is.numeric)
data_numericas <- data[, columnas_numericas]

# Calcular la media en las columnas numéricas
media <- colMeans(data_numericas)

# Imprimir la media por columna
print(media)

```
(f) Create a new data set by imputing the mode in all the columns which have integer type values.


```{r}

# Instalar el paquete DescTools si no está instalado
# install.packages("DescTools")

# Cargar el paquete DescTools
library(DescTools)

load("C:/Proyectos ML/Mineria/Hands_On_2/nueva_data1.Rdata")

data <- as.data.frame(eliminar_na)

# Calcular la moda en todas las columnas del data frame
moda_data <- sapply(data, Mode)

# Imprimir la moda por columna
print(moda_data)



```
(g) Create a new data set by imputing the most frequent value to the column ”nDoors”

```{r}

library(DescTools)

load("C:/Proyectos ML/Mineria/Hands_On_2/nueva_data1.Rdata")

data <- as.data.frame(eliminar_na)
salida <- subset(data , select = nDoors)
#salida <- data$nDoors
#print(salida)
# Calcular la moda de la columna "nDoors"
moda <- Mode(data$nDoors)

data$nDoors[is.na(data$nDoors)] <- moda
print(moda)

```

(h) Combine the three last imputations to obtain a final dataset. Are there any duplicated cases?
```{r , echo = TRUE , comment=" "}

library(DescTools)

load("C:/Proyectos ML/Mineria/Hands_On_2/carIns_final.Rdata")

#data <- as.data.frame(carIns_final)
data <- as.data.frame(eliminar_na)

#calcular la media
#data <- as.data.frame(eliminar_na)
# Seleccionar solo las columnas numéricas
columnas_numericas <- sapply(data, is.numeric)
data_numericas <- data[, columnas_numericas]

# Calcular la media en las columnas numéricas
media <- colMeans(data_numericas)

# Imprimir la media por columna
print("Media")
print(media)

###############

#datos moda
# Calcular la moda en todas las columnas del data frame
moda_data <- sapply(data, Mode)
# Imprimir la moda por columna
print("MOda")
print(moda_data)
##############
# Busacar valores duplicados
# Calcular la media en un data frame
#media <- colMeans(data)

# Calcular la moda en un data frame
#moda <- Mode(data)

# Encontrar valores duplicados entre la media y la moda
valores_duplicados <- intersect(media, moda_data)

# Imprimir los valores duplicados
 print("valores duplicados")
 
 print( valores_duplicados)


```
## **2 Data Pre-Processing**


```{r}
# Instalar y cargar la librería knitr
install.packages("knitr")
library(knitr)

# Crear un data frame de ejemplo
data <- data.frame(
  Column1 = c(1, 2, 3),
  Column2 = c("A", "B", "C")
)

# Formatear los datos en una tabla HTML
tabla_html <- kable(data)

# Guardar la tabla HTML en un archivo
writeLines(tabla_html, "resultados.html")

```









