---
title: '3 Hands On: Data Exploration'
output:
  html_document:
    df_print: paged
  pdf_document: default
---

**1. Summarization**

*Load the data set carIns final. It already has the imputation of missing values.*


(a) Obtain the number of cars by bodyStyle.
```{r}
library(dplyr)
datos <- load("C:/Proyectos ML/Mineria/Hands On_3 Data Exploration/data/carIns_final.Rdata")
data <- as.data.frame(carIns_final)
leerDato<- data%>%group_by(bodyStyle)%>% count()
print(leerDato)
```

```{r}
library(ggplot2)

# Create a bar plot of car counts by bodyStyle
ggplot(data, aes(x = bodyStyle)) +
  geom_bar(fill = "lightblue", color = "black") +
  labs(x = "Body Style", y = "Count") +
  ggtitle("Number of Cars by Body Style") +
  theme_minimal()

```

(b) Obtain the number of cars by bodyStyle and fuelType

```{r}

data %>% group_by(bodyStyle,fuelType)%>% count()


```

(c) Obtain the mean and the standard deviation of the attribute cityMpg by bodyStyle in ascending order.

```{r}

carIns_final %>% group_by(bodyStyle)%>%summarise(cityMpg.mean = mean(cityMpg), cityMpg.sd = sd(cityMpg) )%>% arrange(cityMpg.mean)
``` 

(d) Also by bodyStyle, and for the attributes cityMpg and highwayMpg, obtain the mean, the standard
deviation, the median and the inter-quartile range.

```{r}
library(ggplot2)
  carIns_final %>% group_by(bodyStyle)%>% summarise(cityMpg.mean = mean(cityMpg),
  cityMpg.sd = sd(cityMpg),carretera = IQR(highwayMpg))

```
**2. Visualization**

*Using the package ggplot2, create graphs that you find adequate to answer the following questions*

(e) Show the relationship between the attributes cityMpg and highwayMpg

```{r}
ggplot(carIns_final,aes(x = cityMpg, y = highwayMpg))+geom_point( color = "red")+ggtitle("Relation entre City  & Hightway")
```

(f) Show the distribution of cars by bodyStyle.

```{r}
ggplot(carIns_final,aes(x = bodyStyle))+ geom_bar(fill = "lightblue", color = "black")
```

(g) Show the distribution of cars by price. Suggestion: create bins of width equal to 5000.

```{r}

# Create price bins with a width of 5000
price_bins <- seq(0, max(data$price), by = 5000)

# Cut the prices into bins
price_categories <- cut(data$price, breaks = price_bins, include.lowest = TRUE)
ggplot(carIns_final,aes(x=price_categories))+geom_bar(fill = "lightblue", color = "black")+labs(x = "Price Category", y = "Count") +
  ggtitle("Distribution of Cars by Price")


```

(h) Add the information of the density estimation to the previous graph

```{r}

library(ggplot2)

# Create price bins with a width of 5000
price_bins <- seq(0, max(carIns_final$price), by = 5000)


# Cut the prices into bins
data$price_category <- cut(data$price, breaks = price_bins, include.lowest = TRUE)

# Create a density plot of car prices
ggplot(data, aes(x = price)) +
  geom_density(fill = "lightblue", alpha = 0.5) +
  geom_vline(aes(xintercept = mean(price)), color = "red", linetype = "dashed", size = 1) +
  labs(x = "Price", y = "Density") +
  ggtitle("Density Estimation of Car Prices") +
  theme_minimal()


```

(i) Check (visually) if it is plausible to consider that price follows a normal distribution.

```{r}

library(ggplot2)
library(dplyr)
library(ggfittext)

# Create a histogram with density curve
ggplot(data, aes(x = price)) +
  geom_histogram(binwidth = 5000, fill = "lightblue", color = "black", alpha = 0.5) +
  stat_function(fun = dnorm, args = list(mean = mean(data$price), sd = sd(data$price)), color = "red", size = 1) +
  labs(x = "Price", y = "Frequency") +
  ggtitle("Distribution of Car Prices") +
  theme_minimal()

```

(j) Show the distribution of price by make attribute. Suggestion: use boxplots and the function coord_flip().

```{r}
library(ggplot2)
# Create a boxplot of price by make
ggplot(data, aes(x = make, y = price)) +
  geom_boxplot(fill = "lightblue", color = "black", outlier.shape = NA) +
  coord_flip() +
  labs(x = "Make", y = "Price") +
  ggtitle("Distribution of Price by Make") +
  theme_bw()
```
(k) Show the distribution of price by nDoors attribute. Suggestion: use histograms.
```{r}
library(ggplot2)

# Create a histogram of price by nDoors
ggplot(data, aes(x = price, fill = nDoors)) +
  geom_histogram(binwidth = 2000, color = "black", alpha = 0.9) +
  labs(x = "Price", y = "Count") +
  ggtitle("Distribution of Price by nDoors") + theme_dark()
  

```
(l) Show the distribution of price by bodyStyle and nDoors attributes. Suggestion: use histograms
```{r}
library(ggplot2)

# Create a histogram of price by bodyStyle and nDoors
ggplot(data, aes(x = price, fill = nDoors)) +
  geom_histogram(binwidth = 5000, color = "black", alpha = 0.9) +
  facet_wrap(~ bodyStyle, ncol = 2) +
  labs(x = "Price", y = "Count") +
  ggtitle("Distribution of Price by Body Style and nDoors") +
  theme_bw()

```
(m) Add the parameter scales="free_y" to the facet function in the previous graph.
```{r}
library(ggplot2)

# Create a histogram of price by bodyStyle and nDoors
ggplot(data, aes(x = price, fill = nDoors)) +
  geom_histogram(binwidth = 5000, color = "black", alpha = 1) +
  facet_wrap(~ bodyStyle, scales = "free_y", ncol = 2) +
  labs(x = "Price", y = "Count") +
  ggtitle("Distribution of Price by Body Style and nDoors") +
  theme_minimal()


```





